neonstore: provenance-aware persistent storage for NEON data

### 2022-01-07 paper/paper.Rmd

---
title: "neonstore: provenance-aware persistent storage for NEON data"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Quinn Thomas"
    affiliation: vt
  - name: "Christine Laney"
    affiliation: neon
  - name: "Claire Lunch"
    affiliation: neon
address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: preprint
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
library(neonstore)
#Sys.setenv("NEONSTORE_HOME" = tempfile())
```

@@

>>>>

---
title: "neonstore: provenance-aware persistent storage for NEON data"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Quinn Thomas"
    affiliation: vt
  - name: "Christine Laney"
    affiliation: neon
  - name: "Claire Lunch"
    affiliation: neon
address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: preprint
date: "`r Sys.Date()`"
#bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = FALSE
)
library(neonstore)
#Sys.setenv("NEONSTORE_HOME" = tempfile())
```

@@

```{r include=FALSE}
Sys.unsetenv("AWS_DEFAULT_REGION")
Sys.unsetenv("AWS_S3_ENDPOINT")
Sys.unsetenv("AWS_ACCESS_KEY_ID")
Sys.unsetenv("AWS_SECRET_ACCESS_KEY")
Sys.setenv("AWS_EC2_METADATA_DISABLED"="TRUE")
```
